---
title: "Japanese tourists number"
author: "Suixin Jiang"
date: "3/7/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(MASS)
library(lmtest)
library(tseries)
library(forecast)
```

# Import data
```{r}
jp <- read.csv('TSA.csv')
names(jp)
```


# Time-series variables and then run a linear regression model
```{r}
tour=ts(jp$Amounts.of.tourists,frequency=12,start=c(2010,1),end=c(2018,12))
ex.rate=ts(jp$CNY.JPY,frequency=12,start=c(2010,1),end=c(2018,12))
temp=ts(jp$Average.temperature,frequency=12,start=c(2010,1),end=c(2018,12))
shopmon=ts(jp$Shopping.month,frequency=12,start=c(2010,1),end=c(2018,12))
con.rate=ts(jp$Consumption.rate,frequency=12,start=c(2010,1),end=c(2018,12))

lm.mod=lm(tour~ex.rate+temp+as.factor(shopmon)+con.rate,data=jp)
summary(lm.mod)
dwtest(lm.mod)
```
## The dwtest p-value is very small which indicates autocorrelation problem

# Residuals analysis
```{r}
reslm=lm.mod$residuals
studlm=studres(lm.mod)
fit=lm.mod$fitted.values
```
## QQ plot
```{r}
qqnorm(reslm,pch=20)
qqline(reslm,col='red',lwd=2)
qqnorm(studlm,pch=20)
qqline(studlm,col='red',lwd=2)
```
## Fitted vs. residuals
```{r}
plot(reslm~fit,pch=20)
abline(h=0,lty=2)
plot(studlm~fit,pch=20)
abline(h=0,lty=2)
```
## Non-constant variance check
```{r}
plot(reslm~jp$CNY.JPY,pch=20)
plot(reslm~jp$Average.temperature,pch=20)
plot(reslm~jp$Shopping.month,pch=20)
plot(reslm~jp$Consumption.rate,pch=20)
```

# Since the R-squared is to small then considering ARIMA model
# Split the data into training and testing sets
```{R}
tour.train=ts(jp$Amounts.of.tourists[1:96],frequency=12,
    start=c(2010,1),end=c(2017,12))
tour.test=ts(jp$Amounts.of.tourists[97:108],frequency=12,
    start=c(2018,1),end=c(2018,12))
plot(tour.train)
acf(tour.train, lag.max=50)
pacf(tour.train, lag.max=50)
```

# Plots show seasonality and trend, so we make the 1st differencing to remove trend
```{r}
diff1=diff(tour.train)
plot(diff1)
acf(diff1,lag.max=50)
pacf(diff1,lag.max=50)
model_1=auto.arima(diff1)
model_1
```
## R suggests that model_1 is ARIMA(0,0,2)
```{r}
res_1=model_1$residuals
plot(res_1)
acf(res_1,lag.max=50)
pacf(res_1,lag.max=50)
Box.test(res_1,type='Ljung-Box',fitdf=2,lag=20)
```
## p-value is 0.04655. Then we further difference the training data to remove seasonality
```{r}
diff2=diff(diff1,differences=1,lag=12)
model_2=auto.arima(diff2)
model_2
```
## R suggest that model_2 is ARIMA(0,0,1)(0,0,1)[12]
```{r}
res_2=model_2$residuals
plot(res_2)
acf(res_2,lag.max=50)
pacf(res_2,lag.max=50)
Box.test(res_2,type='Ljung-Box',fitdf=5,lag=20)
```
## P-value is 0.08488, it is still small, so we step back to the beginning to
## Consider further split the data, and only use part of them to train the model
```{r}
tour.train.new=ts(jp$Amounts.of.tourists[52:96],frequency=12,
    start=c(2014,4),end=c(2017,12))
plot(tour.train.new)
acf(tour.train.new,lag.max=50)
pacf(tour.train.new,lag.max=50)
model_3=auto.arima(tour.train.new)
model_3
```
## R suggests model_3 is ARIMA(1,0,0)(0,1,0)[12]
```{r}
res_3=model_3$residuals
plot(res_3,type='p')
acf(res_3,lag.max=50)
pacf(res_3,lag.max=50)
Box.test(res_3,type='Ljung-Box',fitdf=1,lag=20)
```
## p-value is 0.9896, model_3 is accepted
## Then we use testing set to check its accuracy
```{r}
pred18=forecast(model_3,h=12,level=95)
PRED=pred18$mean
LB=pred18$lower
UB=pred18$upper
miny=min(tour.test,PRED,LB,UB)
maxy=max(tour.test,PRED,LB,UB)
plot(tour.test,col='lightgray',type='b',lwd=2,ylim=c(miny,maxy))
lines(PRED,type='b',lty=2,lwd=2)
lines(LB,lty=2,lwd=2,col='red')
lines(UB,lty=2,lwd=2,col='red')
legend('topleft',legend=c('Observed','Predicted','Interval'),lty=c(1,2,2),
    lwd=c(2,1,1),col=c('lightgray','black','red'),bty='n')
```

# Further predict tourists in 2019
```{r}
tour.new=ts(jp$Amounts.of.tourists[52:108],frequency=12,start=c(2014,4),end=c(2018,12))
pred1819=forecast(model_3, h=24, level=95)
PRED1819=pred1819$mean
LB1819=pred1819$lower
UB1819=pred1819$upper
miny1819=min(tour.new, PRED1819,LB1819,UB1819)
maxy1819=max(tour.new, PRED1819,LB1819,UB1819)
plot(tour.new,col='lightgray',type='b',lwd=4,xlim=c(2017,2020),ylim=c(miny1819,maxy1819))
lines(PRED1819,lty=2,lwd=5,type='b')
lines(LB1819,lty=2,lwd=2,col='red')
lines(UB1819,lty=2,lwd=2,col='red')
```

# Predicted tourists number in 2019
```{r}
pred1819
```